

Trained for my Ph.D. and postdoc in California and New York, respectively, I am a beneficiary of a diverse and inclusive research and learning environment, and I am passionate about making my contribution\textemdash in addition to research\textemdash to the broader community of the \appSchool{} through teaching, mentoring, and outreach. I have had the opportunities to teach both undergraduate- and graduate-level courses as a teaching assistant or a guest lecturer, and have developed my teaching philosophy around the visualization and conveyance of ideas while stimulating inspiration. I also recognize the importance of mentoring to a student's intellectual development, which extends far beyond the technical guidance that I can provide, and I have been actively involved in mentoring students at various levels in accordance with their research interests and career goals. I am also a strong advocate for diversity and inclusion, and have worked with, as well as contributed to promoting the accessibility of STEM education to, underrepresented groups in my current and past research programs.

I am excited about the opportunity to join the \appDept{} at the \appSchool{} and contribute to its continued excellence in research and education. I have enclosed my application materials, and will gladly provide any other supporting materials upon request. I hope to have the opportunity to discuss with you further about my qualifications and research visions. Thank you for your consideration and I look forward to hearing from you.

